COG-ED Manuscript

### 2021-11-18 06_Paper/COG-ED/Manuscript.Rmd
changed directory to pilot data folder

  datalist_nback = lapply(list.files(here("04_RawData", "Sampledata"), pattern = '.*nback.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)
  datalist_ED = lapply(list.files(here("04_RawData", "Sampledata"), pattern = '.*_ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)

>>>>

  datalist_nback = lapply(list.files(here("04_RawData", "pilot", "COG-ED"), pattern = '.*nback.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)
  datalist_ED = lapply(list.files(here("04_RawData", "pilot", "COG-ED"), pattern = '.*_ED.*csv', full.names = TRUE),
                          read.csv, stringsAsFactors = FALSE, header = TRUE)
